Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-06-13 emsoft-2019/V2/finite_precision.tex
explicitly say what Daisy does

% introduces roundoff errors, these can be tracked with a dataflow analysis
Finite precision unavoidably introduces roundoff errors, which can accumulate
during the course of a computation.
A sound static roundoff error analysis computes a guaranteed upper bound on the
error of the result by tracking worst-case errors at every operation. Given a
word length for each value, several tools automatically determine the number of
integer bits needed and compute roundoff errors using a dataflow analysis~\cite{Daisy,Gappa}.
They track real-valued ranges at every intermediate operation. These ranges
determine the fixed-point formats and thus also the individual worst-case roundoff errors,
which the analyses track separately from the ranges. To ensure guaranteed
error bounds, both the ranges and errors are computed using interval~\cite{intervals} or
affine arithmetic~\cite{affineArithmetic} which compute sound enclosures. 
Affine arithmetic tracks linear correlations between variables, so for linear expressions
the computed ranges are as tight as possible (nonlinear arithmetic
leads to over-approximations).
% A standard technique to increase accuracy of the computed errors is interval
% subdivision, which divides the input domain into equally-sized subdomains and
% runs roundoff error analysis separately for each subdomain. The
% over-approximations on each subdomain tend to be smaller, which increases the
% overall tightness of range and error bounds.

% mixed-precision tuning
To reduce memory usage and increase efficiency, we want to choose as short word
lengths as possible, \Mahmoud{as this way memory footprint is minimized and run-time is not influenced.} Mixed-precision tuning tools automatically determine possibly different
word lengths for different values~\cite{DaisyTuning,Lee2006}. Compared to uniform precision (or word length),
mixed-precision often leads to improved resource usage, but due to the complexity of
fixed-point arithmetic and the error analysis, is challenging to do manually.  
Automated mixed-precision tuning tools usually perform a search: they repeatedly
select a candidate mixed-precision assignment (i.e. different word lengths for
different values) and check whether the assignment satisfies a given error
bound. The candidate assignments are chosen based on a heuristic which guides
the search towards promising candidates, e.g. using delta-debugging~\cite{DaisyTuning} or
simulated annealing~\cite{Lee2006}.

>>>>

% introduces roundoff errors, these can be tracked with a dataflow analysis
Finite precision unavoidably introduces roundoff errors, which can accumulate
during the course of a computation.
A sound static roundoff error analysis computes a guaranteed upper bound on the
error of the result by tracking worst-case errors at every operation. Given a
word length for each value, several tools\Eva{, including the tool Daisy which we use,} automatically determine the number of
integer bits needed and compute roundoff errors using a dataflow analysis~\cite{Daisy,Gappa}.
They track real-valued ranges at every intermediate operation. These ranges
determine the fixed-point formats and thus also the individual worst-case roundoff errors,
which the analyses track separately from the ranges. To ensure guaranteed
error bounds, both the ranges and errors are computed using interval~\cite{intervals} or
affine arithmetic~\cite{affineArithmetic} which compute sound enclosures. 
Affine arithmetic tracks linear correlations between variables, so for linear expressions
the computed ranges are as tight as possible (nonlinear arithmetic
leads to over-approximations).
% A standard technique to increase accuracy of the computed errors is interval
% subdivision, which divides the input domain into equally-sized subdomains and
% runs roundoff error analysis separately for each subdomain. The
% over-approximations on each subdomain tend to be smaller, which increases the
% overall tightness of range and error bounds.

% mixed-precision tuning
To reduce memory usage and increase efficiency, we want to choose as short word
lengths as possible, \Mahmoud{as this way memory footprint is minimized and run-time is not influenced.} Mixed-precision tuning tools automatically determine possibly different
word lengths for different values~\cite{DaisyTuning,Lee2006}. Compared to uniform precision (or word length),
mixed-precision often leads to improved resource usage, but due to the complexity of
fixed-point arithmetic and the error analysis, is challenging to do manually.  
Automated mixed-precision tuning tools\Eva{, including Daisy,} usually perform a search: they repeatedly
select a candidate mixed-precision assignment (i.e. different word lengths for
different values) and check whether the assignment satisfies a given error
bound. The candidate assignments are chosen based on a heuristic which guides
the search towards promising candidates, e.g. using delta-debugging~\cite{DaisyTuning} or
simulated annealing~\cite{Lee2006}.
